---
title: "Group three - Assignment 1"
author: "Houman Ameri,Sahabe Arbabie, Julio Carneiro"
Date : " August 3rd, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
library(tidyverse)
library(tinytex)
```


## Introduction

This dataset is about Covid analysis

## Load dataset

```{r echo=TRUE}
covid4=read.csv("C:/Users/h.ameri/Desktop/covid4.csv")
```


## Print dataset
```{r echo=TRUE}

print(covid4)
```
## List Variables
```{r echo=TRUE}
names(covid4)

```
## Print top 15 rows
```{r echo=TRUE}
head(covid4, n=15)
```

## User defined function on dataset
```{r echo=TRUE}
testfunction <- function(x,y) {
x+y
}
a=covid4$tot_cases[1]
b=covid4$tot_cases[2]
testfunction(a,b)

```
## Filter rows based on any logical criteria
```{r echo=TRUE}
covid5=as.data.frame(filter(covid4,covid4$new_death>5))
print(covid5)
```
## Reshaping techniques
```{r echo=TRUE}
confirmedcases=covid4$conf_cases
  
probablecases= covid4$prob_cases

totalcases=cbind(confirmedcases,probablecases)

names(totalcases)[1] = "total cases"
names(totalcases)[2] = "probable cases"


print(totalcases)
```
## Remove missing values
```{r echo=TRUE}
is.na(covid4)
```
```{r echo=TRUE}
covid6=as.data.frame(filter(covid4,!is.na(covid4$conf_cases)))
is.na(covid6$conf_cases)
```
## Identify duplicated data 
```{r echo=TRUE}
duplicated(covid4$new_death)
```
## Remove duplicated data 

```{r echo=TRUE}
covid7=as.data.frame(covid4 %>% distinct(covid4$new_case))

covid7

```

## Reorder multiple rows in descending order

```{r}
covid9=as.data.frame(covid7 %>% arrange(desc(covid7)))
covid9
```
## Rename some of the column names

```{r echo=TRUE}
names(covid4)[1] = "name1"
names(covid4)[2] = "name2"


print(covid4)
```
## Adding new variables
```{r echo=TRUE}
covid10=as.data.frame(covid4 %>% mutate(newcolumn = new_death+4))
covid10
```
## Create a training set using random number generator engine

```{r echo=TRUE}
set.seed(143)
covid11=as.data.frame(covid4 %>% sample_n(10, replace = FALSE) )
covid11
```

## Print the summary statistics
```{r echo=TRUE}
summary(covid4)
```
## Calculating Mean

```{r echo=TRUE}
mean(covid4$new_case)
```

## Calculating Median

```{r echo=TRUE}
median(covid4$new_case)
```
## Calculating Mode

```{r echo=TRUE}
mode(covid4$new_case)
```
## Calculating Median
```{r echo=TRUE}
median(covid4$new_case)
```
## Scatter plot for any 2 variables

```{r echo=TRUE}
covid10=as.data.frame(filter(covid10,!is.na(covid10$pnew_death)))
ggplot(data = covid10, aes(x=pnew_death,y=newcolumn))+geom_point(color="steelblue",shape=9)
```
## Scatter bar plot for any 2 variables
```{r echo=TRUE}
ggplot(data=covid10,aes(x=pnew_death,fill=factor(newcolumn)))+geom_bar()
```

## Finding the correlation between any 2 variables

```{r echo=TRUE}
x=covid4[,"tot_death"]
y=covid4[,"new_death"]
xycorr<-cor(x,y,method="pearson")
xycorr
```
## Conclusion

Based on above calculation x and y are correlated

